### 2009-03-02 doc/storage_system/arc-storage-documentation.tex
Added description of how Librarian reads from and writes to replicated A-Hash

TODO: here comes some sentences about how the Librarian reads from any A-Hash and finds the master A-Hash for writing.

>>>>

%TODO: here comes some sentences about how the Librarian reads from any A-Hash and finds the master A-Hash for writing.
The replicated A-Hash deployment is based on a single master, multiple clients scenario (see Section~\ref{sec:a_hash} for details). This means that the Librarian can read from any A-Hash, while it can only write to the master A-Hash. A list of A-Hashes, master and clients, is stored in an A-Hash object. The Librarian periodically gets this list to maintain its own list of A-Hash services. If the Librarian tries to write to the replicated A-Hash and the master is down, the Librarian will try to get a new list from one of the clients and retry the write request once before giving up. In case of reading from the replicated A-Hash, the Librarian will randomly loop through the list of clients until the read request is successful or until there are no more clients available.
